---
title: "session 3"
author: "Patrice"
date: "1/13/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)

mobile <- read_csv("https://raw.githubusercontent.com/vmandela99/Class-assignment-12th-july-2019/master/mobilemoney_data.csv")

skimr::skim(mobile)

summary(mobile)


```

The data has 28 variables and agent trust has 1051 missing values. Highest grade has 256 missing values.

skim::skim(mobile)
the mean hhid is 1597, the mean weight is 443.16, mean age is 37.67

```{r}
#how many account type are there:
mobile %>% count(account_type,sort = T)

```
 Using of %>% is like Then
list of account, we have 7 accounts type
Using <-= assign it to 
to read, use .csv older version, and _csv with the newest version 


Which distrits has many people?
```{r}
# getr the number of people
mobile %>% count(district, sort = T)
```
District_C with 856


  How many count types are there?
```{r}
mobile %>% count(account_type)

mobile %>% count(account_type) %>% ggplot(aes(x = account_type, y = n)) + geom_col() # to put the result in graph

```
  
  
  
what percentage of people from district_A have sacco account?
in the entire data 5.9% are from district A and have sacco account
```{r}
mobile %>% count(district) %>% mutate(percent = n/sum(n)*100) 

mobile %>% count(district, account_type) %>% mutate(percent = n/sum(n)*100) 

mobile %>% filter(district == "District_A") %>% count(account_type) %>% mutate(percent = n/sum(n)*100)

mobile %>% filter(district == "District_A") %>% count(account_type) %>%  mutate(percent = n/sum(n)*100) %>% ggplot (aes(x = account_type, y = n)) + geom_col(fill = "Blue")
# to put a color just add on geom_col(fill = Color)

#there we extract District_A by district == district_A, 
# so from people with sacco Acc they are 18.2 percent

View(mobile)

```

take data, mutate create a new column, put the percentage- n/sum * 100
district A have 32.5

How many grades completed are there?
```{r}
mobile %>% count(highest_grade_completed, sort = T)
```


What is the largest weight in the survey?
```{r}
which.max(mobile$weight)
#
```



What percentage of people are in university and have mobile money account?

```{r}
mobile %>% count(highest_grade_completed, account_type) %>% mutate(percent = n/sum(n)*100) 

mobile %>% filter(highest_grade_completed == "university") %>% count(account_type) %>% mutate(percent = n/sum(n)*100)

mobile %>% filter(highest_grade_completed == "university") %>% count(account_type == "Mobile Money") 


mobile %>% filter(highest_grade_completed == "university") %>% count(account_type == "Mobile Money") %>% mutate(percent = n/sum(n)*100)


```



